Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-29 article.qmd
Add writing models with PySB

Another weakness is related to the way models are written.
While most tools support standards such as the System Biology Markup Language (SBML) [@huckaSBMLL3V2],
no one is expected to write an SBML file directly.
Tellurium uses a Domain Specific Language (DSL) called Antimony [@smithAntimonyModularModel2009],
which can be translated to SBML.
A DSL allows code to be reused in different programming environments,
but it will not be recognized by Integrated Development Environments (IDEs)
and therefore cannot provide the development experience we have come to expect, such as
syntax highlighting, code completion, refactoring, and static analysis.
This has been recognized by the community,
and an extension for Visual Studio Code has been created [@maTestingDynamicalSystems2021].
However, maintaining it in the future could be burdensome for the smaller systems biology community.

>>>>

Another weakness is related to the way models are written.
While most tools support standards such as the System Biology Markup Language (SBML) [@huckaSBMLL3V2],
no one is expected to write an SBML file directly.
Tellurium uses a Domain Specific Language (DSL) called Antimony [@smithAntimonyModularModel2009],
which can be translated to SBML.
A DSL allows code to be reused in different programming environments,
but it will not be recognized by Integrated Development Environments (IDEs)
and therefore cannot provide the development experience we have come to expect, such as
syntax highlighting, code completion, refactoring, and static analysis.
This has been recognized by the community,
and an extension for Visual Studio Code has been created [@maTestingDynamicalSystems2021].
However, maintaining it in the future could be burdensome for the smaller systems biology community.
In the case of PySB,
it leveraged the highly dynamic nature of Python to create a DSL within it.
By default, it uses global state to create species and parameters,
without assigning them to Python variables
or adding them explicitly to the model.
But IDEs cannot understand it and, hence, provide help, as this is not the way they expect Python code to be written.
